Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene

### 2019-05-17 paper/paper.tex
Add changes to paper before resub to NL

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}
% \linenumbers
\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
control transport phenomena at nanometer scale to explore new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes \cite{Karnik_2007,siwy2002fabrication,vlassiouk2007nanofluidic}, field-effect
transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}. Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to the ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using a sheet of nanoporous graphene can
act as a desalination membrane by having the pore sizes smaller than
the hydrated radii ($\sim$1 nm), thereby hindering ion passage without
losing water permeability
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
in practice, the fabrication of subnanometer porous 2D membranes over
a large area with atomic precision remains technically challenging, 
{ limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores or tears can significantly diminish
salt rejection.  Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene, indicating that even large pores ($>$ 30nm) can be ion
selective \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial that if the surface charges can result in a degree of
salt rejection, as the surface charge and potential cannot be
precisely quantified and are sensitive to the surroundings as well as
the history of chemical treatment \cite{Li_2008}. There remains a lack
of fundamental understanding of the interactions between the charged
2D nanopores and the electrolyte solution, { especially in regard of controlled ion transport modulation}.

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by a polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG as schematically shown in
\Fig{} \ref{fig:1}b, using the protocol developed by our group
\cite{Choi_2018} (details see Supplementary Section
\ref{SI-sec:exp}). The normally distributed, circular pores with pore
diameters of 20$\pm$10 nm and a pore density of
1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
over a large area were perforated on graphene.  By optimizing the
subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
characterization of the ion transport behavior (details see
Supplementary Section \ref{SI-sec:exp}).  The system presented here
allows us to systematically investigate the diffusive flux of ions
across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
electrochemical potential in the electrolyte medium.

@@

$x_{r_{i}}$ is the fraction of pores with radius
$r_{i}$ (details see Supplementary Section
\ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
\Fig{} \ref{fig:5}b, the
calculated salt rejection is reduced to $\sim{}$ 80\% of that from the
single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary \Fig{}
\ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
with diameter up to 60 nm, such degree of salt rejection is still
appreciable, which is ascribed to the nonlinear dependency of $\xi$ on

@@

see Supplementary Section \ref{SI-sec:pore-dist}).}

>>>>

\keywords{graphene, nanopore, patterning, salt rejection, gating, finite element modeling, quantum capacitance}

\begin{tocentry}
  \centering
\includegraphics[height=0.40\linewidth]{img/TOC.pdf}
\end{tocentry}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}
% \linenumbers
\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
control transport phenomena at nanometer scale to explore new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes
\cite{Karnik_2007,siwy2002fabrication,vlassiouk2007nanofluidic},
field-effect transistors \cite{Nam_2009}, desalination
\cite{Heiranian_2015}, and nanopore-based DNA sequencing
\cite{Heerema_2016,Garaj_2013}. Porous, atomically thin
two-dimensional (2D) materials, such as graphene, are emerging as
ideal membrane materials due to the ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using a sheet of nanoporous graphene can
act as a desalination membrane by having the pore sizes smaller than
the hydrated radii ($\sim$1 nm), thereby hindering ion passage without
losing water permeability
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}.
Nevertheless, in practice, the fabrication of subnanometer porous 2D
membranes over a large area with atomic precision remains technically
challenging, { limiting the effective separation or demanding
  leak-sealing mechanism such as interfacial polymerization}
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores or tears can significantly diminish
salt rejection. Therefore, it is critical to develop methodology that
allow appreciable selectivity of nanoporous 2D membrane even with
large pore size. Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene, indicating that even large pores ($>$ 30nm) can be ion
selective \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial that if the surface charges can result in a degree of
salt rejection, as the surface charge and potential cannot be
precisely quantified and are sensitive to the surroundings as well as
the history of chemical treatment \cite{Li_2008}. There remains a lack
of fundamental understanding of the interactions between the charged
2D nanopores and the electrolyte solution, { especially in regard of controlled ion transport modulation}.

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by a polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG as schematically shown in
\Fig{} \ref{fig:1}b, using the protocol developed by our group
\cite{Choi_2018}, which enables formation of uniformly-distributed
graphene nanopores over large area up to 25 cm$^{2}$ (details see
Supplementary Section \ref{SI-sec:exp}). The normally distributed,
circular pores with pore diameters of 20$\pm$10 nm and a pore density
of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c
inset) over a large area were perforated on graphene.  By optimizing
the subsequent transfer process, a high surface coverage ($>$ 98\%) of
PG on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
characterization of the ion transport behavior (details see
Supplementary Section \ref{SI-sec:exp}).  The system presented here
allows us to systematically investigate the diffusive flux of ions
across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
electrochemical potential in the electrolyte medium.

@@

$x_{r_{i}}$ is the fraction of pores with radius $r_{i}$ (details see
Supplementary Section \ref{SI-sec:pore-dist}). Combining
Eq. \ref{eq:rejection-comb} and \Fig{} \ref{fig:5}b, the calculated
salt rejection is reduced to $\sim{}$ 80\% of that from the
single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM
(Supplementary \Fig{} \ref{SI-fig:simple-rect-pore}). Consider the
existence of large pores with diameter up to 60 nm, such degree of
salt rejection is still appreciable, which is ascribed to the
nonlinear dependency of $\xi$ on

@@

see Supplementary Section \ref{SI-sec:pore-dist}).}  From our
analysis, it is also clear reducing the average pore size is critical
to overcome the low salt rejection at higher concentrations, which may
hopefully be achieved with more advanced fabrication techniques.

% Therefore, it is critical to develop methodology that
% allow appreciable selectivity of nanoporous 2D membrane even with
% large pore size. Very recently, a number of reports have explored the
% effect of surface charges on the selectivity of ion transport through
% graphene nanopores, as a consequence of the electrostatic interactions
% between solvated ions and the charged functional groups attached on
% graphene, indicating that even large pores ($>$ 30nm) can be ion
% selective \cite{Rollings_2016,Surwade_2014}. However, it remains
% controversial that if the surface charges can result in a degree of
% salt rejection, as the surface charge and potential cannot be
% precisely quantified and are sensitive to the surroundings as well as
% the history of chemical treatment \cite{Li_2008}. There remains a lack
% of fundamental understanding of the interactions between the charged
% 2D nanopores and the electrolyte solution. In this report, we
% investigate electrolyte permeation through graphene nanopores that are
% significantly larger than the hydrated radii. We model the surface
% potential by taking into account of the elementary electronic
% properties of graphene and demonstrate that a high degree of salt
% rejection can be achieved by electrostatic gating.

% \section{Results and discussions}
% \label{sec:res}

% \subsection{Free diffusion through porous graphene}
% \label{sec:res-1}

% \Fig{} \ref{fig:1}a depicts the experimental setup characterizing
% ionic diffusion through a sheet of double layer porous graphene
% (PG). Two reservoirs, namely the high-concentration reservoir (HCR)
% containing electrolyte solution with molar concentration $c_0$, and
% the low-concentration reservoir (LCR) containing de-ionized (DI)
% water, are separated by a PG membrane supported by a polycarbonate
% track-etched (PCTE) film. Magnetic stirrers are used to minimize the
% effects of external concentration polarization, and a conductivity
% probe is placed in the LCR to monitor the ionic concentration as a
% function of time. The membrane is attached to a piece of copper tape
% connected to a voltage source applying an electrical bias
% $V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
% inset). We fabricated the PCTE-supported PG as schematically shown in
% \Fig{} \ref{fig:1}b, using the protocol developed by our group
% \cite{Choi_2018} (details see Supplementary Section
% \ref{SI-sec:exp}). The normally distributed, circular pores with pore
% diameters of 20$\pm$10 nm and a pore density of
% 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
% over a large area were perforated on graphene.  By optimizing the
% subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
% on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
% characterization of the ion transport behavior (details see
% Supplementary Section \ref{SI-sec:exp}).  The system presented here
% allows us to systematically investigate the diffusive flux of ions
% across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
% electrochemical potential in the electrolyte medium.

% First, the control experiments were carried out by measuring the ionic
% diffusion of seven salt species, including KCl, NaCl, LiCl,
% K$_{2}$SO$_{4}$, MgSO$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
% through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
% flux is comparably small, the conductivity increases linearly with
% time in the LCR (e.g. \Fig{} \ref{fig:2}a) within the measurement
% duration (1 h), suggesting the concentration gradient across the
% membrane remains constant. The diffusive fluxes (blue bars in \Fig{}
% \ref{fig:2}b) of different salts were obtained by converting the
% conductivity-time profiles using calibration curves (Supplementary
% Section \ref{SI-sec:measure}). The theoretical diffusive fluxes
% through PCTE are obtained based on the assumption that the membrane
% consists of cylindrical pores with uniform diameter and a low
% tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
% \begin{equation}
%   \label{eq:j-pcte}
%   \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi r_{\mathrm{PCTE}}^{2} N_{\mathrm{p}} D_{\mathrm{\pm}} \Delta c}{L \tau}
% \end{equation}
% where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
% numbers of pore per area, $D_{\mathrm{\pm}}$ is the salt diffusivity
% (average of cation and anion diffusivity), $\Delta c$ is the bulk
% concentration difference between two reservoirs, i.e.,
% $\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
% By using the salt diffusivity values (Supplementary Table
% \ref{SI-tab:diff}), the calculated diffusive fluxes (red bars in
% \Fig{} \ref{fig:2}b) show reasonable agreement with the experimental
% values.

% Next, we carried out the same experiments using the PG-covered PCTE
% membrane (PG-PCTE), without electrostatic gating. The measured
% diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
% \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
% with those of bare PCTE membrane, suggesting that the transport
% resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
% without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
% estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
% $R_{\mathrm{PCTE}}$, i.e.,
% $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
% which is in good agreement with the value derived from the
% experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
% Section \ref{SI-sec:R-model}).

% \subsection{Salt rejection induced by electrostatic gating}
% \label{sec:res-2}

% We next discuss the effects of electrostatic gating on graphene. In
% order to avoid any interference from the conductivity probe to the
% membrane potential, the ``three-interval'' method, which has been used
% in controlling the membrane potential in mesoporous carbon membranes
% \cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
% illustratively represents how the measured conductivity evolves with
% time. Specifically, in the first interval, the gate voltage source is
% turned off and the conductivity probe is on, allowing us to obtain the
% conductivity-time profile with an average slope $s_{1}$ that
% corresponds to the diffusive flux across the PG-PCTE membrane. In the
% second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
% after turning off the conductivity probe, followed by the third
% interval $s_{3}$, in which the conductivity probe is turned on again
% to give the corresponding slope. A control experiment was performed to
% ensure the copper tape was not in direct contact with the ionic
% solution (Supplementary Section \ref{SI-sec:copper}). The slope
% corresponding to the second interval $s_{2}$, as the conductivity
% probe is off, is determined by linear interpolation of the
% conductivities from the endpoint of interval 1 to the starting point
% of interval 3. A decrease of slope observed in interval 2 indicates
% that the total flux through PG-PCTE is reduced upon gating (i.e. salt
% penetration through the PG pores is hindered). We define such
% experimentally measured reduction rate as $\eta$, which is equivalent
% to the decrease of total diffusive flux through PG-PCTE as follows:
% \begin{equation}
%   \label{eq:rejection}
%   \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
%     - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
% \end{equation}
% where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
% $(s_{1} + s_{3})/2$, and
% $\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
% across the PTCE-supported PG double layer as a function of
% $V_{\mathrm{G}}$. Since graphene and PCTE membranes effectively form a
% transport system with series diffusive resistance $R_{\mathrm{G}}$
% (tunable by $V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
% $V_{\mathrm{G}}$), respectively, we define the effective degree of
% salt rejection from bare PG, $\xi$, as a function of $V_{\mathrm{G}}$ (
% details see Supplementary Section \ref{SI-sec:R-model}) as:
% \begin{equation}
% \label{eq:xi-def}
% \xi = 1 - \frac{R_{\mathrm{G}}(V_{\mathrm{G}}=0)}{R_{\mathrm{G}}(V_{\mathrm{G}})} = \frac{(\delta+1) \eta}{\delta \eta + 1}
% \end{equation}
% The factor $\xi$ is a reliable and stable measure of salt rejection
% through the PG membrane itself upon gating, as the salt species and
% initial conditions may induce a degree of measurement uncertainty
% between different samples. Note that the $\xi=1$ limit represents
% perfect salt rejection in which
% $R_{\mathrm{G}}(V_{\mathrm{G}}) \to \infty$. On the contrary $\xi=0$
% indicates $R_{\mathrm{G}}$ remains unchanged with $V_{\mathrm{G}}$.

% Using 0.1 mM KCl solution in HCR, we obtained $\xi$ as a function of
% $V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
% electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
% asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
% a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
% positive carriers (holes) are induced in graphene. We notice that an
% increase of $\xi$, or a decrease of diffusive flux through PG with
% $V_{\mathrm{G}}$, showing an inverse trend compared with those
% observed in ionic field effect transistors (IFETs) in which the
% diffusive flux increases with the gate voltage
% \cite{Nam_2009,Cheng_2018}. A further increase of the KCl
% concentration $c_{0}$ influences the attainable degree of salt
% rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
% $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
% 10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit
% a power law dependency (\Fig{} \ref{fig:2}d). The
% $\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
% law function following
% $\xi_{\mathrm{max}} c_{0}^{0.52} = \mathrm{constant}$. As the Debye
% length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional
% to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced salt
% rejection originates from the modulation of the electrical double
% layer (EDL), as will be discussed later.

% \subsection{Self-consistent ion transport theory}
% \label{sec:theory}

% In order to quantitatively understand the observed $V_{\mathrm{G}}$
% dependence, we develop a theory to model the coupling of graphene's
% elementary transport properties and EDL, in order to quantify the
% ionic transport through a graphene nanopore. Under the assumption that
% the time scale for the bulk concentration change is significantly
% longer than that of ionic diffusion, the pseudo-steady state
% approximation holds. Accordingly, the steady-state Nernst-Planck
% equation describing the ionic transport in an electrolyte solution is
% given by \cite{MacGillivray_1968}:
% \begin{equation}
%   \label{eq:pnp}
%   \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0
% \end{equation}
% where $\boldsymbol{J}$ is the mass flux, subscript \textit{i}
% corresponds to the ionic species (anion or cation), $D$ is the diffusivity,
% $k_{\mathrm{B}}$ is the Boltzmann constant, $T$ is temperature, $c$ is
% the molar concentration, $N_{\mathrm{A}}$ is the Avogadro constant,
% and $\mu_{i}$ is the electrochemical potential. Under the assumption
% of ideal solution, it follows \cite{Kilic_2007}:
% \begin{equation}
%   \label{eq:mu}
%   \nabla \mu_{i} = k_{\mathrm{B}} T \nabla \ln x_{i} + z_{i} e \nabla \psi
% \end{equation}
%  $x$ is the molar fraction in solution, $z$ is the ionic valence,
% $e$ is the unit charge, and $\psi$ is the electric potential. On the
% other hand, the Poisson equation describing the electric potential
% distribution is given by:
% \begin{equation}
%   \label{eq:poisson}
%   \nabla \cdot (\varepsilon_{\mathrm{m}} \varepsilon_{0} \nabla \psi)
%   =
%   - N_{\mathrm{A}} e \sum_{i} c_{i} z_{i}
% \end{equation}
% where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
% individual materials in the system, including water and the internal
% Stern layer\cite{Tian_2017}, and
% $\varepsilon_{0}$ is the vacuum permittivity. When applying
% $V_{\mathrm{G}}$ to graphene adjacent to the electrolyte solution,
% charges (electrons or holes) are induced in graphene; the
% electroneutrality of the entire system suggests:
% \begin{equation}
%   \label{eq:electro-neutral}
%   \sigma_{\mathrm{G}} S_{\mathrm{G}} + \sum_{i} \int_{\Omega} z_{i} c_{i} N_{\mathrm{A}} e \mathrm{d}^{3} \Omega= 0
% \end{equation}
% where $\sigma_{\mathrm{G}}$ is the charge density in graphene,
% $S_{\mathrm{G}}$ is the total area of graphene, and $\Omega$
% corresponds to the entire volumetric domain of electrolyte
% solution. Note that the graphene surface potential,
% $\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to
% change of graphene's work function upon charging, known as the
% graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}
% \ref{fig:3}a) following:
% \begin{equation}
%   \label{eq:Vg}
%   V_{\mathrm{G}} = \Delta \phi_{\mathrm{G}} + \psi_{\mathrm{G}}
% \end{equation}
% where
% $\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
% \phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
% function. The properties of the PG samples fabricated is close to
% intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
% to be 1.4$\times$10$^{11}$ \textit{e}$\cdot$cm$^{-2}$, corresponding
% to a work function difference of 48 meV from graphene's Dirac point
% (details see Supplementary Section \ref{SI-sec:charge-dens}), much
% smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
% Therefore we adapt the simplification that the charge neutrality point
% of graphene coincides with the Dirac point at $V_{\mathrm{G}}$ =
% 0. The elementary electronic properties of graphene give:
% \begin{equation}
%   \label{eq:delta-phiG}
%   \Delta \phi_{\mathrm{G}} = \mathrm{sign}(\sigma_{\mathrm{G}}) \frac{\hbar v_{\mathrm{F}}}{e}
%   \sqrt{\frac{\pi |\sigma_{\mathrm{G}}|}{e}}
% \end{equation}
% where $\hbar$ is the reduced Planck constant, and
% $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
% velocity of graphene (more details find Supplementary Section
% \ref{SI-sec:charge-dens}).  Note that the PG film fabricated
% experimentally is double-layer turbostratic (randomly aligned)
% graphene, in which we assume the
% $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
% Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
% self-consistently by discretizing
% Eqs. \eqref{eq:pnp}-\eqref{eq:poisson} using the finite-element method
% (FEM), in which the graphene surface potential is coupled with
% Eqs. \eqref{eq:electro-neutral}-\eqref{eq:delta-phiG} that were solved
% simultaneously to reach convergent numerical solutions of
% $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ for a given
% $V_{\mathrm{G}}$. Clearly, the above model yields symmetric
% characteristics for $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ with
% respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
% graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene
% synthesized by chemical vapor deposition (CVD) used in our
% experiments, it is well-recognized that the electron traps are
% inherently introduced during synthesis and patterning
% \cite{Dean_2010}, effectively reducing the charge density and surface
% potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{}
% \ref{SI-fig:trap}), which is related to the fact that observed $\xi$
% is much lower within the $V_{\mathrm{G}}<0$ regime in \Fig{}
% \ref{fig:2}c. With the nonideality in mind, hereafter, we compare the
% calculations and experiments in the regime of $V_{\mathrm{G}}>0$. For
% example, \Fig{} \ref{fig:3}c presents the calculated
% $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function of
% $V_{\mathrm{G}}$ considering the ionic diffusion through a single 20
% nm-diameter nanopore drilled on a sheet of semi-infinite double layer
% graphene that separates HCR containing KCl solution at $c_{0}$ = 0.1
% mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
% Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay
% between graphene quantum capacitance and the EDL significantly reduces
% the graphene surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
% $V_{\mathrm{G}}$ = 1.25 V, corresponding a surface charge density
% $\sigma_{\mathrm{G}}$ of $\sim$0.08 C$\cdot$m$^{-2}$. Note that as we
% mentioned earlier, an important merit of the 2D nanopore system
% considered here is that the surface charge density can be precisely
% determined and controlled, rather than being treated as a fitting
% parameter as in most of the 2D nanopore literature
% (e.g. Ref. \citenum{Rollings_2016}). In addition, we anticipate that
% the gate-controlled ionic transport can also be achieved by replacing
% graphene with other nanoporous conducting 2D materials, although the
% operational gate voltage window required to achieve the same degree of
% salt rejection may be narrower, because graphene has the smallest
% quantum capacitance (near the Dirac point) among all known 2D
% materials \cite{Tian_2016}.

% \subsection{Salt rejection mechanism}
% \label{sec:mechanism}

% The numerical procedure described above allows us to resolve the
% concentration and electric potential profiles near a graphene
% nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
% by both $\psi$ and $c$ fields (see Eq. \eqref{eq:pnp} and \eqref{eq:mu}),
% we focus on the electrochemical potential $\mu_{i}$, which represents
% the combined driving force, to reveal its dependence on the applied
% $V_{\mathrm{G}}$. Following the same system considered in \Fig{}
% \ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
% and the relative electrochemical potentials,
% $\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
% $V_{\mathrm{G}}$ = 0.75 V are shown in \Fig{} \ref{fig:4}a and
% \ref{fig:4}b, respectively. The reference point of the electrochemical
% potentials is set at the bulk phase in the HCR. As expected, the
% electric potential reaches the maximum at the graphene surface (with
% $\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
% solution phase, forming an EDL surrounding the graphene surface. Since
% the Debye length $\lambda_{\mathrm{D}}$ is comparable to the
% pore radius $r_{\mathrm{G}}$, the electric potential at the nanopore
% center remains at $\sim$25 mV, comparable to the thermal energy at
% room temperature ($k_{\mathrm{B}}T$ = 26 meV). Consequently, it is
% evident that the potential barrier is sufficient to modulate the
% diffusive flux.

% We further reveal the cation and anion transport pathways by looking
% into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
% increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
% graphene surface reduces the cation concentration at the pore edge due
% to the electrostatic interactions, thereby increasing its
% concentration gradient at the pore center. On the other hand, the
% anion concentration near the pore edge increases exponentially, such
% that the concentration gradient at the pore center becomes small (see
% Supplementary Section \ref{SI-sec:conc}, Supplementary
% Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}). Although the surface
% concentration of anions is enhanced by $\sim{}$30 times, it is sill
% much smaller than the saturated surface adsorption density, and the
% bulk diffusivity used in the Nernst-Planck equation still holds.  We
% also observe that $\Delta \mu_{+}$ is dominated by the concentration,
% while $\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the
% balance between the diffusion and drift potentials (see Supplementary
% Section \ref{SI-sec:conc}, Supplementary Figs.  \ref{SI-fig:potential}
% and \ref{SI-fig:flux}). The observations confirm the distinct ionic
% transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
% center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
% presents the calculated \textit{z}-component of the cation and anion
% fluxes through the pore at the graphene plane (z = 0),
% $\boldsymbol{J}_{z}$ ,as a function of the normalized radius,
% $r/r_{\mathrm{G}}$ , where $r$ is the radial coordinate and
% $r_{\mathrm{G}}$ is the pore radius, at different $V_{\mathrm{G}}$
% values. Note that $\boldsymbol{J}_{z}$ is negative because the LCR is
% placed at z$<$0 in the simulation box. At $V_{\mathrm{G}}$ = 0 (pure
% diffusion), the anion and cation flux profiles are identical, with a
% higher flux near the pore edge, which is expected, as the
% concentration gradient is higher. By gradually increasing
% $V_{\mathrm{G}}$, both fluxes are reduced throughout the pore, while
% the degree of reduction is more pronounced at the pore edge for the
% cation, and at the pore center for the anion, following the scenarios
% we discussed above. Accordingly, the integrated fluxes across the
% pore, $|\boldsymbol{J}_{z}|$, are reduced with $V_{\mathrm{G}}$
% (\Fig{} \ref{fig:4}d). A total flux reduction of $\sim$90\% is
% predicted. Another interesting finding here is that, by increasing
% $V_{\mathrm{G}}$, the nanopore transport preferentially allows cations
% over anions, or in other words, the anion flux is more reduced with
% $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the ion
% selectivity of graphene nanopore \cite{Rollings_2016}. In our setup,
% the imbalance between cation and anion fluxes near the graphene
% nanopore is compensated by the EDL formation at the counter-electrode
% in LCR, which maintains the electroneutrality of the system. Notably,
% since atomically thin graphene samples are used, the mechanism of salt
% rejection is clearly distinct from that in capacitive deionization
% \cite{Biesheuvel_2010}, where electrodes with large surface area are
% required. More detailed discussion about the selective ionic pathways
% upon gating can be found in Supplementary Section \ref{SI-sec:conc}.

% The above mechanistic findings, nevertheless, do not fully clarify the
% experimentally observed reduction of diffusive flux upon
% gating. Indeed, the same physical mechanism also governs the ionic
% transport through an IFET, in which a nonzero electric potential at
% the nanopore center usually results in an increase of ionic
% conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
% further increased the graphene surface potential $\psi_{\mathrm{G}}$
% considering the same system (details see Supplementary Section
% \ref{SI-sec:conc}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
% larger than 400 mV, the ionic flux starts to increase, reversing the
% trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
% drift flux become dominant over diffusion flux and (ii) the
% concentration near the pore edge (preferred path) greatly increases
% (details see Supplementary Section \ref{SI-sec:conc}, Supplementary
% Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
% $\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
% membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
% triggers the electrochemical reactions \cite{Toh_2011}. On the other
% hand, in an IFET, the electric potential on the pore wall is
% considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
% metallic nature of gate electrode (having an infinitely-large quantum
% capacitance). We therefore conclude that the quantum
% capacitance-induced nonlinear damping in the surface potential results
% in the observed salt rejection.  Following the above discussions, we
% further investigate the physical limits for the biased graphene
